---
title: "WA Exposure Sites"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---
<!-- Adjusting Font Type for Styles to Arial -->
<style type="text/css">

body{ /* Normal  */
  font-family: Arial, Helvetica, sans-serif;
  }
td {  /* Table  */
  font-family: Arial, Helvetica, sans-serif;
}
h1.title {
  font-family: Arial, Helvetica, sans-serif;
}
h1 { /* Header 1 */
  font-family: Arial, Helvetica, sans-serif;
}
h2 { /* Header 2 */
  font-family: Arial, Helvetica, sans-serif;
}
h3 { /* Header 3 */
  font-family: Arial, Helvetica, sans-serif;
}
p {
  display: inline
}
.dataTables_scrollBody {
    max-height: 100% !important;
}
</style>

```{r setup, include=FALSE}
library(data.table)
library(magrittr)
library(leaflet)
library(flexdashboard)
library(crosstalk)
library(DT)
# library(summarywidget)

# folder <- 'C:/Users/pli/Documents/COVID/'
# folder <- 'C:/Users/zdtf0342/Documents/wacovid/'
folder <- Sys.getenv('WACOVID-FOLDER')

Health_Advice_Mapping <- fread(paste0(folder, 'data/Health_Advice_Mapping.csv'), encoding = 'UTF-8')
sites <- fread(paste0(folder, 'data/Sites.csv'), encoding = 'UTF-8')
sites_by_day <- fread(paste0(folder, 'data/Sites_by_Day.csv'), encoding = 'UTF-8')

sites_by_day[is.na(Date_Time_Day), Date_Time_Day := as.Date('2022-01-04')]

sites[, Health_Advice_Short := as.factor(Health_Advice_Short)]
sites[, Suburb := as.factor(Suburb)]
sites_by_day[, Health_Advice_Short := as.factor(Health_Advice_Short)]
sites_by_day[, Suburb := as.factor(Suburb)]
```

By Day
======================================================================

Row {data-height=200}
-----------------------------------------------------------------------

### Chart B {.no-title}

```{r}
labels <- sites_by_day[, paste0(Date_Time, '\n', Location)]
sites_by_day[, label := labels]

shared_sites_by_day <- SharedData$new(sites_by_day[!is.na(lon), .(Date_Time, Suburb, Location, Date_updated, Health_Advice_Short, Date_Time_Day, lon, lat, Marker_Color, label)])

bscols(
  list(
    filter_slider("exposure_date", "Exposure Date", shared_sites_by_day, ~Date_Time_Day, step = 1, width = "100%"),
    filter_checkbox("health_advice", "Health Advice", shared_sites_by_day, ~Health_Advice_Short, inline = TRUE)
  )
)
```


Row {data-height=800 .tabset}
-----------------------------------------------------------------------

### Map 

```{r}

leaflet(height = 1000) %>%
  addTiles() %>%
  addAwesomeMarkers(
    data = shared_sites_by_day,
    lng = ~lon,
    lat = ~lat,
    icon = awesomeIcons(
      icon = 'ios-close',
      library = 'ion',
      markerColor = ~Marker_Color
    ),
    label = ~label
  )
```


### Table

```{r}
datatable(
    data = shared_sites_by_day,
    # extensions = 'Buttons',
    options = list(
      autoWidth = TRUE,
      # columnDefs = list(list(width = '100px', targets = '_all')),
      dom = 't',
      # buttons = c('copy', 'csv'),
      ordering = TRUE,
      paging = FALSE,
      columnDefs = list(list(visible=FALSE, targets=c(5:9))),
      initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'font-family': 'arial', 'font-size': '12px', 'text-align': 'center','vertical-align': 'middle','padding-top': '0px','padding-bottom': '0px','padding-left': '0px','padding-right': '0px'});",
        "}"
      )
    ),
    rownames = FALSE, 
    colnames = c('Date and Time of Exposure' = 'Date_Time',
                 'Last Updated' = 'Date_updated',
                 'Health Advice' = 'Health_Advice_Short'),
    selection = 'none',
    filter = 'top'
  ) %>%
    formatStyle(
      c('Date and Time of Exposure', 'Suburb', 'Location', 'Last Updated', 'Health Advice'),
      fontFamily = 'arial',
      fontSize = '12px',
      color = "#000000",
      fontWeight = 'normal',
      verticalAlign = 'middle',
      paddingTop = '0px',
      paddingBottom = '0px',
      paddingLeft = '10px',
      paddingRight = '10px'
    )
```



All Exposure Sites
======================================================================

Row {data-width=1000 .tabset}
-----------------------------------------------------------------------

### Map

```{r}
addAwesomeMarkers_for_Marker_Color <- function(map, color) {
  data.filt <- sites[!is.na(lon) & Marker_Color == color, .(Date_Time, Location, Suburb, Date_updated, Health_advice, Health_Advice_Short, Marker_Color, lon, lat)]
  labels <- data.filt[, paste0(
    "<strong>Exposure Date & Time</strong><br/>", Date_Time,
    "<br/><strong>Location</strong><br/>", Location,
    "<br/><strong>Suburb</strong><br/>", Suburb,
    "<br/><strong>Date Updated</strong><br/>", Date_updated,
    "<br/><strong>Health Advice</strong><br/>", Health_advice)]
  labels <- gsub('\t', '', labels)
  labels <- gsub('\n\n', '<br/>', labels)
  labels <- gsub('\n', '<br/>', labels)
  labels <- gsub('<br/>.<br/>', '<br/>', labels)
  labels <- labels %>% lapply(htmltools::HTML)
  
  addAwesomeMarkers(
    map,
    data = data.filt,
    group = ~Health_Advice_Short,
    lng = ~lon,
    lat = ~lat,
    icon = ~awesomeIcons(
      icon = 'ios-close',
      library = 'ion',
      markerColor = Marker_Color
    ),
    # clusterOptions = markerClusterOptions(maxClusterRadius = 0.01, spiderfyDistanceMultiplier = 1.5),
    label = labels
  )
}

leaflet(height = 1000) %>%
  addTiles() %>%
  addAwesomeMarkers_for_Marker_Color('black') %>%
  addAwesomeMarkers_for_Marker_Color('red') %>%
  addAwesomeMarkers_for_Marker_Color('yellow') %>%
  addAwesomeMarkers_for_Marker_Color('blue') %>%
  addLayersControl(
    overlayGroups = Health_Advice_Mapping[, Health_Advice_Short],
    options = layersControlOptions(collapsed = FALSE)
  )
```

### Table

```{r}
datatable(
    data = sites[,.(Date_Time, Suburb, Location, Date_updated, Health_Advice_Short)],
    # extensions = 'Buttons',
    options = list(
      autoWidth = TRUE,
      # columnDefs = list(list(width = '100px', targets = '_all')),
      dom = 't',
      # buttons = c('copy', 'csv'),
      ordering = TRUE,
      paging = FALSE,
      initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'font-family': 'arial', 'font-size': '12px', 'text-align': 'center','vertical-align': 'middle','padding-top': '0px','padding-bottom': '0px','padding-left': '0px','padding-right': '0px'});",
        "}"
      )
    ),
    rownames = FALSE,
    colnames = c('Date and Time of Exposure' = 'Date_Time',
                 'Last Updated' = 'Date_updated',
                 'Health Advice' = 'Health_Advice_Short'),
    selection = 'none',
    filter = 'top'
  ) %>%
    formatStyle(
      c('Date and Time of Exposure', 'Suburb', 'Location', 'Last Updated', 'Health Advice'),
      fontFamily = 'arial',
      fontSize = '12px',
      color = "#000000",
      fontWeight = 'normal',
      verticalAlign = 'middle',
      paddingTop = '0px',
      paddingBottom = '0px',
      paddingLeft = '10px',
      paddingRight = '10px'
    )
```


All (Heatmap)
======================================================================

Row {data-width=1000}
-----------------------------------------------------------------------

### Heatmap of Exposure Sites

```{r}
leaflet(height = 1000) %>%
  addTiles() %>%
  # addAwesomeMarkers_for_Marker_Color('black') %>%
  # addAwesomeMarkers_for_Marker_Color('red') %>%
  # addAwesomeMarkers_for_Marker_Color('yellow') %>%
  # addAwesomeMarkers_for_Marker_Color('blue') %>%
  leaflet.extras::addHeatmap(
    data = sites[!is.na(lon)],
    lng = ~lon,
    lat = ~lat,
    intensity = ~Health_Advice_Severity/4,
    radius = 15,
    blur = 15,
    group = 'Heat Map'
  ) # %>%
  # leaflet.extras::addHeatmap(
  #   data = sites[1],
  #   lng = ~lon,
  #   lat = ~lat,
  #   intensity = NA,
  #   radius = 0,
  #   blur = 0,
  #   group = 'No Heat Map'
  # ) %>%
  # addLayersControl(
  #   baseGroups = c('Heat Map', 'No Heat Map'),
  #   overlayGroups = c(Health_Advice_Mapping[, Health_Advice_Short]),
  #   options = layersControlOptions(collapsed = FALSE)
  # )
```


